Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-08-01 doc/ms.tex
Include updated figures in the manuscript
Update paper to include new figures as well as corresponding captions

\begin{figure*}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{logLC_with_colors.pdf}
  \caption{Photometric evolution of \abc. \textit{Top}: The $g$-band
  light curve of \abc. Observations from different 
  telescopes are shown with different symbols. Time is measured in 
  rest-frame d relative to the time of first light, $t_0$ (see 
  \S\ref{sec:lc_fit}). Note that the horizontal axis is shown with a linear scale 
  for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; \mathrm{d}$ and a 
  $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. The solid curve 
  represents the best-fit model from SALT2 
  (\S\ref{sec:classification}). The black ticks near the
  bottom of the panel show epochs of spectroscopic observations.
  \textit{Bottom}: Color curves of \abc. Each color curve is 
  represented with a different color, with each symbol corresponding 
  to a different instrument, as detailed in the legend. Magnitude 
  offsets applied to each color curve are also shown.
  }
  \label{fig:lightcurve}
\end{figure*}

@@

\begin{figure*}[!htb]
  \centering
  \includegraphics[width=1.0\textwidth]{spectra.pdf}
  \caption{Observed spectral sequence of \abc. The spectra are 
  normalized by their median flux between 6,000 and 
  7,000$\,\textrm{\AA}$.  The phase of each spectrum 
  relative to $T_{B_\mathrm{max}}$ is shown. Telluric absorption
  bands are grayed out. Line identifications are provided for 
  the spectral features discussed in the text. 
  For clarity, high-resolution spectra obtained with the VLT have been omitted (see Ferretti et al.\ 2017, submitted, for a detailed discussion of these spectra).}
  \label{fig:spec_seq}
\end{figure*}

@@

\begin{figure*}[!htb]
  \centering
  \includegraphics[width=0.95\textwidth]{early_lc.pdf}
  \caption{Best-fit power-law model to describe the early flux from 
  \abc\ in the $g_\mathrm{PTF}$-band. The model flux, adopting 
  best-fit parameters $\alpha=0.98$ and $t_0=-17.94\,\textrm{d}$, 
  is shown as a solid black line in the top panel. The lower panel 
  shows the model residuals, and the symbols are the same as in
  Figure~\ref{fig:lightcurve}. The model is fit to just the 
  $g_\mathrm{PTF}$-band observations to avoid systematic difference 
  between the filters (see the text for further 
  details). The joint distribution of $t_0$ and $\alpha$ is 
  illustrated in the inset of the upper panel. The solid and 
  dashed contours represent the $68\%$ and $99.7\%$ confidence 
  levels.
  }
  \label{fig:early_lc_fit}
\end{figure*}

@@

\begin{figure*}[!thb]
  \centering
  \includegraphics[width=0.45\textwidth]{Chi2.pdf}
  \includegraphics[width=0.45\textwidth]{VelocityPlot.pdf}
  \caption{Constraints on $t_{exp}$ from fitting the velocity
    evolution of \ion{Si}{2}.
    \textit{Left panel:} the dashed, solid
    and dash-dotted curves show $\chi^2$ for fitting power laws with
    indices $-0.20$, $-0.22$ and $-0.24$, respectively. The blue
    vertical line and the orange shaded region indicate $t_0$ and its
    95\% confidence interval from Section
    \ref{sec:lc_fit}, respectively.
    \textit{Right panel:} Observed \ion{Si}{2}\,$\lambda$6355
    velocities (blue circles) and the best-fit power-law model
     with an index of $-0.22$ (dashed line). Additionally the 
     measured velocites of \ion{C}{2}\,$\lambda\lambda$6580, 7234 
     are shown.}
  \label{fig:velocity_t_exp}
\end{figure*}

@@

Similar to our analysis of the \ion{Si}{2}\,$\lambda$6355 line, we 
can measure velocities and pseudo-equivalent widths (pEWs) of 
\ion{C}{2}\,$\lambda\lambda$6580, 7234. We compare the velocity 
evolution of the \ion{C}{2} lines to \ion{Si}{2} in the right panel 
of Figure \ref{fig:velocity_t_exp} and the pEW evolution is
shown in Figure \ref{fig:ew}. These measurements confirm the qualitative analysis from Figure~\ref{fig:carbon}: namely, the pEW of \ion{C}{2}\,$\lambda$6580 is comparable to that
of \ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \; \mathrm{d}$ and 
the pEW of \ion{C}{2} 
decreases until the feature is no longer detectable 
around $t = -10$ d.

\begin{figure}[]
  \centering
  \includegraphics[width=0.45\textwidth]{pEW.pdf}
  \caption{Evolution of the pseudo-equivalent width of 
  \ion{Si}{2}\,$\lambda$6355, and \ion{C}{2}\,$\lambda\lambda$6580, 
  7234 in the week following explosion.}
  \label{fig:ew}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.45\textwidth]{16abc_11fe_colors.pdf}
  \caption{$(B - V)_0$ color evolution of \abc\ (shown as squares) 
    compared to SN\,2011fe (shown as stars). The $B$ and $V$ 
    photometry are calibrated on the Vega system. The data for 
    SN\,2011fe are from \citet{2016ApJ...820...67Z}.}
  \label{fig:B-Vcolors}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{iPTF16abc_Ni_lc.pdf}
  \caption{Photometric comparison of \abc\ and the theoretical 
  models of \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni 
  mixing in the SN ejecta increases from the short-dash, dark lines 
  to the long-dash, light lines.
  \textit{Top}: $M_g$ vs.\ time, where the observed $g$-band 
  magnitudes  
  have been corrected to $M_g$ using the distance modulus to \abc\ 
  (\S\ref{sec:host})
  and the total line-of-site reddening ($E(B-V) = 0.078 \; 
  \mathrm{mag}$; Ferretti et al.\ 2017, submitted).
  \textit{Bottom}: $(g' - r')_0$ vs.\ time. The observed colors have 
  been corrected for reddening.
  }
  \label{fig:Ni56LC}
\end{figure}

@@

>>>>

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.48\textwidth]{logLC_with_colors.pdf}
  \caption{The $g$-band
  light curve of \abc. Observations from different 
  telescopes are shown with different symbols. Time is measured in 
  rest-frame d relative to the time of first light, $t_0$ (see 
  \S\ref{sec:lc_fit}). Note that the horizontal axis is shown with 
  a linear scale for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; 
  \mathrm{d}$ and a $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. 
  The black ticks near the
  bottom of the panel show epochs of spectroscopic observations.
  }
  \label{fig:lightcurve}
\end{figure}

@@

\begin{figure*}[!htb]
  \centering
  \includegraphics[width=0.8\textwidth]{spectra.pdf}
  \caption{Observed spectral sequence of \abc. The spectra are 
  normalized by their median flux between 6,000 and 
  7,000$\,\textrm{\AA}$.  The phase of each spectrum 
  relative to $T_{B_\mathrm{max}}$ is shown. Telluric absorption
  bands are grayed out. Line identifications are provided for 
  the spectral features discussed in the text. 
  For clarity, high-resolution spectra obtained with the VLT have been omitted (see Ferretti et al.\ 2017, submitted, for a detailed discussion of these spectra).}
  \label{fig:spec_seq}
\end{figure*}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.48\textwidth]{early_lc.pdf}
  \caption{Best-fit power-law model to describe the early flux from 
  \abc\ in the $g_\mathrm{PTF}$-band. The model flux, adopting 
  best-fit parameters $\alpha=0.98$ and $t_0=-17.94\,\textrm{d}$, 
  is shown as a solid black line in the top panel. The lower panel 
  shows the model residuals, and the symbols are the same as in
  Figure~\ref{fig:lightcurve}. The model is fit to just the 
  $g_\mathrm{PTF}$-band observations to avoid systematic difference 
  between the filters (see the text for further 
  details). The joint distribution of $t_0$ and $\alpha$ is 
  illustrated in the inset of the upper panel. The solid and 
  dashed contours represent the $68\%$ and $99.7\%$ confidence 
  levels.
  }
  \label{fig:early_lc_fit}
\end{figure}

@@

\begin{figure*}[!thb]
  \centering
  \includegraphics[width=0.48\textwidth]{Chi2.pdf}
  \includegraphics[width=0.48\textwidth]{VelocityPlot.pdf}
  \caption{Constraints on $t_{exp}$ from fitting the velocity
    evolution of \ion{Si}{2}.
    \textit{Left panel:} the dashed, solid and dash-dotted curves 
    show $\chi^2$ for fitting power laws with
    indices $-0.20$, $-0.22$ and $-0.24$, respectively. The blue
    vertical line and the orange shaded region indicate $t_0$ and 
    its 95\% confidence interval from Section
    \ref{sec:lc_fit}, respectively.
    \textit{Right panel:} Observed \ion{Si}{2}\,$\lambda$6355
    velocities (blue circles) and the best-fit power-law model
     with an index of $-0.22$ (dashed line). Additionally the 
     measured velocites of \ion{C}{2}\,$\lambda\lambda$6580, 7234 
     are shown. \textit{Right inset}: Evolution of the 
     pseudo-equivalent width of \ion{Si}{2}\,$\lambda$6355, and 
     \ion{C}{2}\,$\lambda\lambda$6580, 7234 in the week following 
     explosion.}
  \label{fig:velocity_t_exp}
\end{figure*}

@@

Similar to our analysis of the \ion{Si}{2}\,$\lambda$6355 line, we 
can measure velocities and pseudo-equivalent widths (pEWs) of 
\ion{C}{2}\,$\lambda\lambda$6580, 7234. We compare the velocity 
evolution of the \ion{C}{2} lines to \ion{Si}{2} in the right panel 
of Figure \ref{fig:velocity_t_exp}, which also shows the pEW evolution of these lines. These measurements confirm the qualitative analysis from Figure~\ref{fig:carbon}: namely, the pEW of \ion{C}{2}\,$\lambda$6580 is comparable to that
of \ion{Si}{2}\,$\lambda$6355 at $t \approx -16 \; \mathrm{d}$ and 
the pEW of \ion{C}{2} 
decreases until the feature is no longer detectable 
around $t = -10$ d.

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{16abc_11fe_colors.pdf}
  \caption{$(B - V)_0$ color evolution of \abc\ (shown as squares) 
    compared to SN\,2011fe (shown as stars). The $B$ and $V$ 
    photometry are calibrated on the Vega system, and have been 
    corrected for extinction. The data for 
    SN\,2011fe are from \citet{2016ApJ...820...67Z}.}
  \label{fig:B-Vcolors}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{iPTF16abc_Ni_lc.pdf}
  \caption{Photometric comparison of \abc\ and the theoretical 
  models of \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni 
  mixing in the SN ejecta increases from the short-dash, dark lines 
  to the long-dash, light lines.
  \textit{Top}: $M_g$ vs.\ time, where the observed $g$-band 
  magnitudes  
  have been corrected to $M_g$ using the distance modulus to \abc\ 
  (\S\ref{sec:host})
  and the total line-of-site reddening ($E(B-V) = 0.078 \; 
  \mathrm{mag}$; Ferretti et al.\ 2017, submitted). The orange 
  solid line shows the model with the most $^{56}$Ni mixing 
  shifted to an explosion time of $t_0 - 0.4 \; \mathrm{d}$. This 
  model provides a good match to the data.
  \textit{Bottom}: $(g' - r')_0$ vs.\ time. The observed colors 
  have been corrected for reddening.
  }
  \label{fig:Ni56LC}
\end{figure}

@@

\appendix

\section{Photometric Light Curves}

The full photometric light curves of \abc\ are shown in Figure~\ref{fig:ugly_LC}.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.48\textwidth]{lightcurve.pdf}
  \caption{UV, optical, and NIR light curves for \abc. 
  \textit{Top}: $BVgri$ light curves from the P48, P60, and LCO-1m 
  telescopes. The solid lines represent the best-fit model from 
  SALT2 (see \ref{sec:classification}).
  \textit{Bottom}: UV and NIR light curves from the \textit{Swift} 
  and SPM-1.5m telescopes, respectively.
  For both panels each light curve is represented with a different 
  color, while the different symbols correspond to different 
  instruments, as detailed in the legends. The legends also list 
  offsets applied to each light curve. Photometry is shown in the 
  AB mag system, with the exception of the $BV$ bands, which are 
  shown in the Vega system. The photometry shown has not been 
  corrected for line-of-sight extinction.
  }
  \label{fig:ugly_LC}
\end{figure}
